Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-05 mr-review.Rmd
added section header
wrote about sensitivity analysis

@@

>>>>

@burgess_sensitivity_2017 divided the suite of methods for sensitivity analysis 
into two categories: 1) those that support the validity of causal inferences in a MR 
study and 2) those that question that validity. Because not all confounding variables are known or measured, assumptions 2 and 3 are not fully verifiable 
in MR studies. Recognition of this fact has inspired the development of 
sensitivity analysis tools. While we can't assess whether a SNP instrument is 
associated with every confounder of the exposure-outcome association, it is 
possible to examine the associations of the SNP instrument with the measured 
covariates. While absence of such associations doesn't guarantee satisfaction 
of the assumption, presence of SNP-covariate associations must be investigated
carefully, as they may constitute assumption violations [@burgess_sensitivity_2017].

@@

## Statistical models and methods for MR with multiple instruments and one outcome
